Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-17 writeup/gz_hubble_data.tex
adding flags to Task 01 in datatables and description of such in text

The GZH catalog is corrected for classification bias only for the first
question of the GZH decision tree (Section~\ref{sec:debiasing}), which asks
{\it ``Is the galaxy smooth and round, with no sign of a disk?''} For this
question, the catalog provides the additional parameters $\tt debiased$, $\tt
lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions. The $\tt best$
fraction for \ffeatures{} is chosen based on the categorization of the galaxy:
if it is ``correctable'', $\tt best = debiased$; if it is a lower limit, 
$\tt best = lower~limit$; if neither condition applies, then 
$\tt best = weighted$.

@@

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrllllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for \hst{} images from AEGIS, COSMOS, GEMS, and GOODS\label{tbl:catalog_hst}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Project ID} & 
\colhead{Hubble ID} & 
\colhead{Imaging} & 
\colhead{Correction$^{1}$} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{}
}
\small
\startdata
AHZ100002g  & 10010842  & AEGIS             & 0        & 127       & 0.118    & 0.128     & 0.085    & 0.085    & 0.226     & 0.226    \\
AHZ100002h  & 10010870  & AEGIS             & 4        & 127       & 0.567    & 0.592     & 0.927    & 0.592    & $-$       & $-$      \\
$\ldots$    \\
AHZ20004kd  & 20014731  & COSMOS            & 3        &  44       & 0.682    & 0.675     & 0.147    & 0.675    & $-$       & $-$      \\
AHZ20004ke  & 20014732  & COSMOS            & 2        &  45       & 0.689    & 0.756     & 0.893    & 0.756    & $-$       & $-$      \\
$\ldots$    \\
AHZ400043g  & 90022729  & GEMS              & 1        & 121       & 0.702    & 0.733     & 0.487    & 0.734    & 0.483     & 0.800    \\
AHZ4000416  & 90022735  & GEMS              & 1        & 127       & 0.646    & 0.698     & 0.508    & 0.698    & 0.171     & 0.727    \\
$\ldots$    \\
AGZ0007z47  & 10014     & GOODS-N-FULLDEPTH & 1        & 40        & 0.475    & 0.475     & 0.197    & 0.475    & 0.011     & 0.496    \\
AGZ0007z48  & 10017     & GOODS-N-FULLDEPTH & 3        & 40        & 0.675    & 0.675     & 0.048    & 0.675    & 0.168     & 0.669    \\
$\ldots$    \\
AGZ00083jb  & 8869      & GOODS-S-FULLDEPTH & 1        & 40        & 0.425    & 0.425     & 0.109    & 0.425    & 0.070     & 0.548    \\
AGZ00083jc  & 8878      & GOODS-S-FULLDEPTH & 0        & 40        & 0.205    & 0.205     & 0.048    & 0.048    & $-$0.005  & 0.287    \\
$\ldots$    \\
\enddata
\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were
corrected through debiasing (Section~\ref{ssec:zeta_results}), if possible.
0~=~correctable, 1~=~lower-limit ($f_{raw}$ --- $f_{adj}$ is not
single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrected
(insufficient \ferengi{} galaxies in this $z$-$\mu$ bin), 4~=~uncorrected (no
galaxy redshift available).}
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 118,425~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

@@

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrllllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for color-faded Hubble images\label{tbl:catalog_faded}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Project ID} & 
\colhead{Hubble ID} & 
\colhead{Imaging} & 
\colhead{Correction} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{}
}
\small
\startdata
AHZF000001  &   20000002    &   COSMOS  &   1   &   48 &  0.708   &     0.755   &   0.228    &    0.754 &   0.325   &   0.829  \\
AHZF000003  &   20000004    &   COSMOS  &   3   &   49 &  0.367   &     0.379   &   0.100    &    0.379 &   0.198   &   0.198  \\
AHZF000004  &   20000006    &   COSMOS  &   3   &   49 &  0.265   &     0.271   &   0.010    &    0.270 &   $-$	    &   $-$    \\
AHZF00000z  &   20000102    &   COSMOS  &   1   &   44 &  0.727   &     0.78    &   0.233    &    0.780 &   0.316   &   0.820  \\
AHZF000010  &   20000104    &   COSMOS  &   2   &   53 &  0.811   &     0.849   &   0.904    &    0.848 &   $-$	    &   $-$    \\
$\ldots$    \\
\enddata
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 3,927~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrllllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for color-inverted Hubble images\label{tbl:catalog_recolored}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Project ID} & 
\colhead{Hubble ID} & 
\colhead{Imaging} & 
\colhead{Correction} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{}
}
\small
\startdata
AHZC000001	&   20000002	&   COSMOS	&   1	&   168	&   0.615   &   0.664   &   0.160   &  0.663   &  0.271    &  0.775    \\
AHZC000003	&   20000004	&   COSMOS	&   0	&   235	&   0.333   &   0.364   &   0.002   &  0.002   &  0.063    &  0.063    \\
AHZC000004	&   20000006	&   COSMOS	&   3	&   316	&   0.235   &   0.252   & $-0.011$  &  0.252   &  $-$	    &  $-$      \\
AHZC00000z	&   20000102	&   COSMOS	&   1	&   207	&   0.755   &   0.757   &   0.272   &  0.756   &  0.249    &  0.796    \\
AHZC000010	&   20000104	&   COSMOS	&   2	&   158	&   0.843   &   0.882   &   0.936   &  0.881   &  $-$	    &  $-$      \\
$\ldots$    \\
\enddata
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 3,927~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrllllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for GOODS 2-epoch images\label{tbl:catalog_goods_shallow}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & &  
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Project ID} & 
\colhead{Hubble ID} & 
\colhead{Imaging} & 
\colhead{Correction} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{}
}
\small
\startdata
AHZ3000001  &   50000000    &     GOODS-N   &   0   &   123	&   0.390   &   0.415	&   0.090 &   0.090 &   $-$     &   $-$      \\
AHZ3000002  &   50000001    &     GOODS-N   &   2   &   126	&   0.341	&   0.355	&   0.356 &   0.356 &   0.220	&   0.279    \\
AHZ3000003  &   50000005    &     GOODS-N   &   1   &   129	&   0.760   &   0.826	&   0.633 &   0.825 &   0.596	&   0.834    \\
AHZ3000004  &   50000008    &     GOODS-N   &   1   &   120	&   0.758	&   0.787	&   0.639 &   0.787 &   0.658	&   0.834    \\
AHZ3000005  &   50000010    &     GOODS-N   &   1   &   123	&   0.854	&   0.890   &   0.611 &   0.889 &   0.597	&   0.914    \\
$\ldots$    \\
\enddata
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 6,144~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for SDSS Stripe 82 single-epoch images\label{tbl:stripe82_single}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{4}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Project ID} & 
\colhead{SDSS DR7 ObjID} & 
\colhead{Imaging} & 
\colhead{Correction} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{}
}
\small
\startdata
AHZ5000001  &   587730845812064684  &   SDSS    &     2 &   41  &   0.585   &    0.595  &   0.759   &   0.594   \\
AHZ5000002  &   587730845812065247  &   SDSS    &     2 &   46  &   0.609   &    0.651  &   0.897   &   0.651   \\
AHZ5000003  &   587730845812196092  &   SDSS    &     2 &   51  &   0.039   &    0.044  &   0.067   &   0.043   \\
AHZ5000004  &   587730845812196825  &   SDSS    &     2 &   35  &   0.514   &    0.605  &   0.928   &   0.605   \\
AHZ5000005  &   587730845812524122  &   SDSS    &     2 &   47  &   0.766   &    0.812  &   1.038   &   0.810   \\
AHZ5000006  &   587730845812654984  &   SDSS    &     2 &   42  &   0.5	    &    0.542  &   0.680   &   0.541   \\
AHZ5000007  &   587730845812655541  &   SDSS    &     2 &   41  &   0.488   &    0.526  &   0.697   &   0.525   \\
AHZ5000008  &   587730845812720365  &   SDSS    &     2 &   53  &   0.792   &    0.84   &   1.050   &   0.839   \\
AHZ5000009  &   587730845812720640  &   SDSS    &     4 &   43  &   0.0	    &    0.0    &   0.0	    &   0.0	    \\
AHZ500000a  &   587730845812720699  &   SDSS    &     2 &   40  &   0.425   &    0.478  &   0.588   &   0.477   \\
$\ldots$    \\
\enddata
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 21,522~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for SDSS Stripe 82 co-added images\label{tbl:stripe82_coadd}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{4}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Project ID} & 
\colhead{SDSS DR7 ObjID} & 
\colhead{Imaging} & 
\colhead{Correction} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{}
}
\small
\startdata
AHZ6000001  & 8647474690312306978   &   SDSS    &    4  & 40  & 0.275   &    0.289  &   0.762   &   0.289   & \\
AHZ6000002  & 8647474690312307154   &   SDSS    &    2  & 43  & 0.605   &    0.634  &   0.858   &   0.635   & \\
AHZ6000003  & 8647474690312307877   &   SDSS    &    2  & 51  & 0.608   &    0.627  &   0.906   &   0.627   & \\
AHZ6000004  & 8647474690312308301   &   SDSS    &    4  & 52  & 0.038   &    0.038  &   0.723   &   0.038   & \\
AHZ6000005  & 8647474690312308318   &   SDSS    &    2  & 44  & 0.614   &    0.632  &   0.776   &   0.631   & \\
AHZ6000006  & 8647474690312308880   &   SDSS    &    2  & 36  & 0.667   &    0.683  &   0.901   &   0.683   & \\
AHZ6000007  & 8647474690312372644   &   SDSS    &    4  & 48  & 0.646   &    0.674  &   1.145   &   0.674   & \\
AHZ6000008  & 8647474690312372789   &   SDSS    &    4  & 45  & 0.489   &    0.571  &   0.964   &   0.570   & \\
AHZ6000009  & 8647474690312372931   &   SDSS    &    4  & 47  & 0.553   &    0.587  &   0.926   &   0.587   & \\
AHZ600000a  & 8647474690312373190   &   SDSS    &    4  & 47  & 0.574   &    0.559  &   1.008   &   0.559   & \\
$\ldots$    \\
\enddata
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 30,339~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

>>>>

The GZH catalog is corrected for classification bias only for the first
question of the GZH decision tree (Section~\ref{sec:debiasing}), which asks
{\it ``Is the galaxy smooth and round, with no sign of a disk?''} For this
question, the catalog provides the additional parameters $\tt debiased$, $\tt
lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions. The $\tt best$
fraction for \ffeatures{} is chosen based on the categorization of the galaxy:
if it is ``correctable'', $\tt best = debiased$; if it is a lower limit, 
$\tt best = lower~limit$; if neither condition applies, then 
$\tt best = weighted$. Flags are also given for the three responses of Task 01 to identify clean samples of galaxies with high likelihoods of being smooth, featured, or an artifact.  These are set as $\tt smooth/featured/artifact\_flag=1$ if $\rm f_{smooth/features/artifact\_best}>0.8$. For a galaxy to be flagged as ``smooth'', an additional criterion of $\tt correction\_type =~$0, 1, or 2 is applied. This is to account for the uncertainty in distinguishing between genuine ellipticals and disks whose features have been washed out due to surface brightness and redshift effects, as described in Section~\ref{sec:debiasing}.

@@

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrlllllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for \hst{} images from AEGIS, COSMOS, GEMS, and GOODS\label{tbl:catalog_hst}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{7}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Zooniverse ID} & 
\colhead{Survey ID} & 
\colhead{Imaging} & 
\colhead{Correction$^{1}$} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{flag} &
\colhead{}
}
\small
\startdata
AHZ100002g  & 10010842  & AEGIS             & 0        & 127       & 0.118    & 0.128     & 0.085    & 0.085    & 0.226     & 0.226 & 0   \\
AHZ100002h  & 10010870  & AEGIS             & 4        & 127       & 0.567    & 0.592     & 0.927    & 0.592    & $-$       & $-$   &0   \\
$\ldots$    \\
AHZ20004kd  & 20014731  & COSMOS            & 3        &  44       & 0.682    & 0.675     & 0.147    & 0.675    & $-$       & $-$   &0   \\
AHZ20004ke  & 20014732  & COSMOS            & 2        &  45       & 0.689    & 0.756     & 0.893    & 0.756    & $-$       & $-$   &0   \\
$\ldots$    \\
AHZ400043g  & 90022729  & GEMS              & 1        & 121       & 0.702    & 0.733     & 0.487    & 0.734    & 0.483     & 0.800 &0   \\
AHZ4000416  & 90022735  & GEMS              & 1        & 127       & 0.646    & 0.698     & 0.508    & 0.698    & 0.171     & 0.727 &0   \\
$\ldots$    \\
AGZ0007z47  & 10014     & GOODS-N-FULLDEPTH & 1        & 40        & 0.475    & 0.475     & 0.197    & 0.475    & 0.011     & 0.496 &0   \\
AGZ0007z48  & 10017     & GOODS-N-FULLDEPTH & 3        & 40        & 0.675    & 0.675     & 0.048    & 0.675    & 0.168     & 0.669 &0  \\
$\ldots$    \\
AGZ00083jb  & 8869      & GOODS-S-FULLDEPTH & 1        & 40        & 0.425    & 0.425     & 0.109    & 0.425    & 0.070     & 0.548 &0   \\
AGZ00083jc  & 8878      & GOODS-S-FULLDEPTH & 0        & 40        & 0.205    & 0.205     & 0.048    & 0.048    & $-$0.005  & 0.287 &0   \\
$\ldots$    \\
\enddata
\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were
corrected through debiasing (Section~\ref{ssec:zeta_results}), if possible.
0~=~correctable, 1~=~lower-limit ($f_{raw}$ --- $f_{adj}$ is not
single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrected
(insufficient \ferengi{} galaxies in this $z$-$\mu$ bin), 4~=~uncorrected (no
galaxy redshift available).}
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 118,425~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

@@

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrlllllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for color-faded Hubble images\label{tbl:catalog_faded}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{7}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Zooniverse ID} & 
\colhead{Survey ID} & 
\colhead{Imaging} & 
\colhead{Correction} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{flag} &
\colhead{}
}
\small
\startdata
AHZF000001  &   20000002    &   COSMOS  &   1   &   48 &  0.708   &     0.755   &   0.228    &    0.754 &   0.325   &   0.829 &0 \\
AHZF000003  &   20000004    &   COSMOS  &   3   &   49 &  0.367   &     0.379   &   0.100    &    0.379 &   0.198   &   0.198 &0 \\
AHZF000004  &   20000006    &   COSMOS  &   3   &   49 &  0.265   &     0.271   &   0.010    &    0.270 &   $-$	    &   $-$   &0 \\
AHZF00000z  &   20000102    &   COSMOS  &   1   &   44 &  0.727   &     0.78    &   0.233    &    0.780 &   0.316   &   0.820 &0 \\
AHZF000010  &   20000104    &   COSMOS  &   2   &   53 &  0.811   &     0.849   &   0.904    &    0.848 &   $-$	    &   $-$   &0 \\
$\ldots$    \\
\enddata
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 3,927~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrllllllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for color-inverted Hubble images\label{tbl:catalog_recolored}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{7}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Zooniverse ID} & 
\colhead{Survey ID} & 
\colhead{Imaging} & 
\colhead{Correction} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{flag} &
\colhead{}
}
\small
\startdata
AHZC000001	&   20000002	&   COSMOS	&   1	&   168	&   0.615   &   0.664   &   0.160   &  0.663   &  0.271    &  0.775 &0   \\
AHZC000003	&   20000004	&   COSMOS	&   0	&   235	&   0.333   &   0.364   &   0.002   &  0.002   &  0.063    &  0.063 &0   \\
AHZC000004	&   20000006	&   COSMOS	&   3	&   316	&   0.235   &   0.252   & $-0.011$  &  0.252   &  $-$	    &  $-$  &1    \\
AHZC00000z	&   20000102	&   COSMOS	&   1	&   207	&   0.755   &   0.757   &   0.272   &  0.756   &  0.249    &  0.796 &0   \\
AHZC000010	&   20000104	&   COSMOS	&   2	&   158	&   0.843   &   0.882   &   0.936   &  0.881   &  $-$	    &  $-$  &1    \\
$\ldots$    \\
\enddata
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 3,927~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrlllllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for GOODS 2-epoch images\label{tbl:catalog_goods_shallow}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & &  
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{7}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Zooniverse ID} & 
\colhead{Survey ID} & 
\colhead{Imaging} & 
\colhead{Correction} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{flag} &
\colhead{}
}
\small
\startdata
AHZ3000001  &   50000000    &     GOODS-N   &   0   &   123	&   0.390   &   0.415	&   0.090 &   0.090 &   $-$     &   $-$ &0     \\
AHZ3000002  &   50000001    &     GOODS-N   &   2   &   126	&   0.341	&   0.355	&   0.356 &   0.356 &   0.220	&   0.279 &0   \\
AHZ3000003  &   50000005    &     GOODS-N   &   1   &   129	&   0.760   &   0.826	&   0.633 &   0.825 &   0.596	&   0.834 &0   \\
AHZ3000004  &   50000008    &     GOODS-N   &   1   &   120	&   0.758	&   0.787	&   0.639 &   0.787 &   0.658	&   0.834 &0   \\
AHZ3000005  &   50000010    &     GOODS-N   &   1   &   123	&   0.854	&   0.890   &   0.611 &   0.889 &   0.597	&   0.914 &0  \\
$\ldots$    \\
\enddata
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 6,144~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrlllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for SDSS Stripe 82 single-epoch images\label{tbl:stripe82_single}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{5}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Zooniverse ID} & 
\colhead{Survey ID} & 
\colhead{Imaging} & 
\colhead{Correction} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{flag} &
\colhead{}
}
\small
\startdata
AHZ5000001  &   587730845812064684  &   SDSS    &     2 &   41  &   0.585   &    0.595  &   0.759   &   0.594 &0  \\
AHZ5000002  &   587730845812065247  &   SDSS    &     2 &   46  &   0.609   &    0.651  &   0.897   &   0.651 &0  \\
AHZ5000003  &   587730845812196092  &   SDSS    &     2 &   51  &   0.039   &    0.044  &   0.067   &   0.043 &0  \\
AHZ5000004  &   587730845812196825  &   SDSS    &     2 &   35  &   0.514   &    0.605  &   0.928   &   0.605 &0  \\
AHZ5000005  &   587730845812524122  &   SDSS    &     2 &   47  &   0.766   &    0.812  &   1.038   &   0.810 &1  \\
AHZ5000006  &   587730845812654984  &   SDSS    &     2 &   42  &   0.5	    &    0.542  &   0.680   &   0.541 &0  \\
AHZ5000007  &   587730845812655541  &   SDSS    &     2 &   41  &   0.488   &    0.526  &   0.697   &   0.525 &0  \\
AHZ5000008  &   587730845812720365  &   SDSS    &     2 &   53  &   0.792   &    0.84   &   1.050   &   0.839 &1  \\
AHZ5000009  &   587730845812720640  &   SDSS    &     4 &   43  &   0.0	    &    0.0    &   0.0	    &   0.0   &0    \\
AHZ500000a  &   587730845812720699  &   SDSS    &     2 &   40  &   0.425   &    0.478  &   0.588   &   0.477 &0  \\
$\ldots$    \\
\enddata
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 21,522~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrlllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for SDSS Stripe 82 co-added images\label{tbl:stripe82_coadd}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{5}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Zooniverse ID} & 
\colhead{Survey ID} & 
\colhead{Imaging} & 
\colhead{Correction} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{flag} &
\colhead{}
}
\small
\startdata
AHZ6000001  & 8647474690312306978   &   SDSS    &    4  & 40  & 0.275   &    0.289  &   0.762   &   0.289   & 0&\\
AHZ6000002  & 8647474690312307154   &   SDSS    &    2  & 43  & 0.605   &    0.634  &   0.858   &   0.635   & 0&\\
AHZ6000003  & 8647474690312307877   &   SDSS    &    2  & 51  & 0.608   &    0.627  &   0.906   &   0.627   & 0&\\
AHZ6000004  & 8647474690312308301   &   SDSS    &    4  & 52  & 0.038   &    0.038  &   0.723   &   0.038   & 0&\\
AHZ6000005  & 8647474690312308318   &   SDSS    &    2  & 44  & 0.614   &    0.632  &   0.776   &   0.631   & 0&\\
AHZ6000006  & 8647474690312308880   &   SDSS    &    2  & 36  & 0.667   &    0.683  &   0.901   &   0.683   & 0&\\
AHZ6000007  & 8647474690312372644   &   SDSS    &    4  & 48  & 0.646   &    0.674  &   1.145   &   0.674   & 0&\\
AHZ6000008  & 8647474690312372789   &   SDSS    &    4  & 45  & 0.489   &    0.571  &   0.964   &   0.570   & 0&\\
AHZ6000009  & 8647474690312372931   &   SDSS    &    4  & 47  & 0.553   &    0.587  &   0.926   &   0.587   & 0&\\
AHZ600000a  & 8647474690312373190   &   SDSS    &    4  & 47  & 0.574   &    0.559  &   1.008   &   0.559   & 0&\\
$\ldots$    \\
\enddata
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 30,339~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}
